raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-10-13 code/rmarkdown/article.Rmd
+ minor ref fix

<!-- biodiversity processes are important -->
Prioritisations must capture the ecological and evolutionary processes that sustain biodiversity [@r3; @r255; @r9]. Ecological processes are important for biodiversity to persist over short time-scales. For instance, predator-prey processes can mediate ecosystem structure and function through top-down control [@r476]. Additionally, migratory processes allow many species to access suitable habitat throughout the year [@r477]. On the other hand, evolutionary processes are important for biodiversity to persist over long time-scales. Adaptive evolutionary processes foster resilience against environmental change [@r3; @r43], and neutral evolutionary processes maintain genetic diversity [@r5; @r67; @r63]. In recent decades, a wealth of data relevant to biodiversity processes has become available [eg. bioclimatic, distribution, genetic, phylogenetic, and trait data; @r406; @r33; @r460; @r453]. This is sparked significant interest in using this data to make better conservation decisions [@r68; @r9; @r473; @r247; @r448; @r468; @r407; @r61; @r2; @r470; @r475; @r469].

>>>>

<!-- biodiversity processes are important -->
Prioritisations must capture the ecological and evolutionary processes that sustain biodiversity [@r3; @r255; @r9]. Ecological processes are important for biodiversity to persist over short time-scales. For instance, predator-prey processes can mediate ecosystem structure and function through top-down control [@r476]. Additionally, migratory processes allow many species to access suitable habitat throughout the year [@r477]. On the other hand, evolutionary processes are important for biodiversity to persist over long time-scales. Adaptive evolutionary processes foster resilience against environmental change [@r3; @r43], and neutral evolutionary processes maintain genetic diversity [@r5; @r67; @r63]. In recent decades, a wealth of data relevant to biodiversity processes has become available [eg. bioclimatic, distribution, genetic, phylogenetic, and trait data; @r406; @r33; @r460; @r453]. This is sparked significant interest in using this data to make better conservation decisions [@r68; @r9; @r473; @r247; @r448; @r468; @r2; @r407; @r61; @r470; @r475; @r469].
